Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-07-25 alloscore_manuscript/alloscore-application-shorter.tex

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Thu Feb 29 18:53:54 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
\texttt{CU-select} & 669 & 133 & 774 & 326 \\ 
  \texttt{per-capita} & 865 & - & 1029 & 366 \\ 
  \texttt{COVIDhub-ensemble} & 873 & 159 & 1067 & 438 \\ 
  \texttt{USC-SI\_kJalpha} & 995 & 91 & 1216 & 1097 \\ 
  \texttt{JHUAPL-Gecko} & 1034 & 164 & 1141 & 418 \\ 
  \texttt{MUNI-ARIMA} & 1084 & 169 & 1248 & 440 \\ 
  \texttt{COVIDhub-trained\_ensemble} & 1089 & 169 & 1271 & 823 \\ 
  \texttt{COVIDhub-baseline} & 1175 & 170 & 1317 & 535 \\ 
  \texttt{JHUAPL-Bucky} & 1358 & 102 & 1566 & 1214 \\ 
  \texttt{JHUAPL-SLPHospEns} & 1540 & 129 & 1604 & 1102 \\ 
  \texttt{UVA-Ensemble} & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS), (see Section \ref{sec:ias_examp}). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Thu Feb 29 18:53:58 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
model & MAS & taMWIS & taMWIS rank \\ 
  \hline
\texttt{COVIDhub-ensemble} & 389 & 70 & 2 \\ 
  \texttt{per-capita} & 464 & - & - \\ 
  \texttt{COVIDhub-trained\_ensemble} & 483 & 87 & 4 \\ 
  \texttt{CU-select} & 502 & 81 & 3 \\ 
  \texttt{JHUAPL-SLPHospEns} & 526 & 67 & 1 \\ 
  \texttt{COVIDhub-baseline} & 594 & 93 & 5 \\ 
  \texttt{JHUAPL-Bucky} & 643 & 112 & 7 \\ 
  \texttt{MUNI-ARIMA} & 707 & 116 & 8 \\ 
  \texttt{JHUAPL-Gecko} & 929 & 110 & 6 \\ 
  \texttt{USC-SI\_kJalpha} & 1473 & 155 & 9 \\ 
   \hline
\end{tabular}
\caption{Time averaged mean weighted interval scores (taMWIS) and mean allocation scores (MAS) by model across 13 weeks. These results show the average performance across time for the nine models that submitted forecasts for every week from 2021-11-29 through 2022-02-21, as well
  as for a per-capita allocation. MWIS is not defined for the \texttt{per-capita} allocation which does not use forecasts.} 
\label{tab:multi-week-performance-summary}
\end{table}

@@

We define
$$G^{\star}(F) := \argmin_{G \in \mathcal{P}_{sec:propriety_of_parametric_approximation\mathrm{dfq}}} E_{F}[S_A(G, Y)].$$
Since $S_R$ is defined as the Bayes scoring rule for the forecaster's loss \eqref{eqn:forecaster_theta_loss}, $G^{\star}(F)$ coincides
with $G_{\theta^{\star}(F)}$, the distribution in $\mathcal{P}_{\mathrm{dfq}}$ given by the
optimal submission parameters $\theta^{\star}(F)$ for the forecaster with predictive distribution $F$.
In general, $G^q(F)$ and $G^\star(F)$ will be different distributions:  matching $F$ at specific quantiles
does not require $G^q(F)$ to match $F$ at the quantiles for $\tau^{F,K}$ (c.f. \eqref{eqn:quantiles-sum-to-K}),
which would be necessary for it to share $x^F$ as an optimal allocation.

>>>>

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Mar  1 16:18:50 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
\texttt{CU-select} & 669 & 133 & 774 & 326 \\ 
  \texttt{per-capita} & 865 & - & 1029 & 366 \\ 
  \texttt{COVIDhub-ensemble} & 873 & 159 & 1067 & 438 \\ 
  \texttt{USC-SI\_kJalpha} & 995 & 91 & 1216 & 1097 \\ 
  \texttt{JHUAPL-Gecko} & 1034 & 164 & 1141 & 418 \\ 
  \texttt{MUNI-ARIMA} & 1084 & 169 & 1248 & 440 \\ 
  \texttt{COVIDhub-trained\_ensemble} & 1089 & 169 & 1271 & 823 \\ 
  \texttt{COVIDhub-baseline} & 1175 & 170 & 1317 & 535 \\ 
  \texttt{JHUAPL-Bucky} & 1358 & 102 & 1566 & 1214 \\ 
  \texttt{JHUAPL-SLPHospEns} & 1540 & 129 & 1604 & 1102 \\ 
  \texttt{UVA-Ensemble} & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS), (see Section \ref{sec:ias_examp}). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Mar  1 16:18:55 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
model & MAS & taMWIS & taMWIS rank \\ 
  \hline
\texttt{COVIDhub-ensemble} & 389 & 70 & 2 \\ 
  \texttt{per-capita} & 464 & - & - \\ 
  \texttt{COVIDhub-trained\_ensemble} & 483 & 87 & 4 \\ 
  \texttt{CU-select} & 502 & 81 & 3 \\ 
  \texttt{JHUAPL-SLPHospEns} & 526 & 67 & 1 \\ 
  \texttt{COVIDhub-baseline} & 594 & 93 & 5 \\ 
  \texttt{JHUAPL-Bucky} & 643 & 112 & 7 \\ 
  \texttt{MUNI-ARIMA} & 707 & 116 & 8 \\ 
  \texttt{JHUAPL-Gecko} & 929 & 110 & 6 \\ 
  \texttt{USC-SI\_kJalpha} & 1473 & 155 & 9 \\ 
   \hline
\end{tabular}
\caption{Time averaged mean weighted interval scores (taMWIS) and mean allocation scores (MAS) by model across 13 weeks. These results show the average performance across time for the nine models that submitted forecasts for every week from 2021-11-29 through 2022-02-21, as well
  as for a per-capita allocation. MWIS is not defined for the \texttt{per-capita} allocation which does not use forecasts.} 
\label{tab:multi-week-performance-summary}
\end{table}

@@

We define
$$G^{\star}(F) := \argmin_{G \in \mathcal{P}_{\mathrm{dfq}}} E_{F}[S_A(G, Y)].$$
Since $S_R$ is defined as the Bayes scoring rule for the forecaster's loss \eqref{eqn:forecaster_theta_loss}, $G^{\star}(F)$ coincides
with $G_{\theta^{\star}(F)}$, the distribution in $\mathcal{P}_{\mathrm{dfq}}$ given by the
optimal submission parameters $\theta^{\star}(F)$ for the forecaster with predictive distribution $F$.
In general, $G^q(F)$ and $G^\star(F)$ will be different distributions:  matching $F$ at specific quantiles
does not require $G^q(F)$ to match $F$ at the quantiles for $\tau^{F,K}$ (c.f. \eqref{eqn:quantiles-sum-to-K}),
which would be necessary for it to share $x^F$ as an optimal allocation.
